\documentclass[11pt]{article}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{geometry}
\usepackage{array}
\usepackage{longtable}
\geometry{margin=1in}

\setcounter{secnumdepth}{0}
\newcommand{\cmark}{$\checkmark$}
\newcommand{\xmark}{$\times$}

\title{AMC 12 Teacher Report: April 23--26, 2026}
\author{}
\date{}

\begin{document}
\maketitle

\section{Grading Summary}

\textbf{Scope.} Rows 1--15 of \texttt{amc12-2026-04\_student.csv} were completed. Rows 16--50 were not attempted yet and were left blank in the redo CSV.

\textbf{Timing standard.} Use the student's AMC12 pacing rule: Questions 1--10 should average 2:00 each, Questions 11--15 should average 3:00 each, Questions 16--20 should stay near a 4:00 cap, and selected Questions 21--25 may receive up to 5:00 only when progress is clear. Since this worksheet contains Problem 10 items, the target budget is 2:00 per problem. Correct answers over 2:00 are treated as speed-review items, not redo items.

\section{AMC12 Pace Strategy}

\begin{longtable}{@{}>{\raggedright\arraybackslash}p{0.24\textwidth} >{\centering\arraybackslash}p{0.18\textwidth} >{\centering\arraybackslash}p{0.18\textwidth} >{\raggedright\arraybackslash}p{0.32\textwidth}@{}}
\textbf{Question Band} & \textbf{Target} & \textbf{Checkpoint} & \textbf{Decision Rule}\\
\hline
Q1--Q10 & 2:00 each & 20:00 total & Build a time bank. If there is no clear path after 90 seconds, mark it and move.\\
Q11--Q15 & 3:00 each & 35:00 total & Solve cleanly, but skip if still setting up after 2.5 minutes.\\
Q16--Q20 & Up to 4:00 each & 55:00 total & Attempt only while progress is visible; otherwise save the time for later.\\
Q21--Q25 & Selective, up to 5:00 & Final 20:00 & Do not spend 5 minutes on all five. Choose accessible problems and return to flagged work.\\
\end{longtable}

\textbf{Important caveat.} A flat allocation of 2 minutes for Q1--Q10, 3 minutes for Q11--Q15, and 5 minutes for every Q16--Q25 problem totals \(20+15+50=85\) minutes, which exceeds the 75-minute AMC12 limit. Therefore the 5-minute rule for Q16--Q25 is a maximum for selected problems, not a promise to attempt all ten hard problems fully.

\section{Systematic Speed Methodologies for Instruction}

\textbf{Teaching objective.} Do not train the student to ``rush.'' Train the student to reduce the number of decisions made under time pressure. The guides in \texttt{guides} consistently point to the same system: classify quickly, execute one clean first method, pivot before algebra expands, verify at the right depth, and log the trigger that should be recognized faster next time.

\subsection{Two-Minute Operating System for Problem 10}

For the current worksheet, every item is a Problem 10 item, so the working target is 2:00. Use the following routine until it becomes automatic.

\begin{longtable}{@{}>{\raggedright\arraybackslash}p{0.12\textwidth} >{\raggedright\arraybackslash}p{0.24\textwidth} >{\raggedright\arraybackslash}p{0.28\textwidth} >{\raggedright\arraybackslash}p{0.28\textwidth}@{}}
\textbf{Time} & \textbf{Teacher Cue} & \textbf{In the Head} & \textbf{On Scratch Paper}\\
\hline
0--15s & Classify before solving. & Read for domain, objective, answer-choice shape, and confidence. Ask: algebra, geometry, counting, number theory, probability, or sequence? & Problem number; one domain tag; one technique cue such as ``Vieta,'' ``PoP,'' ``cycle,'' ``mean,'' ``faces.''\\
15--35s & Make the first move. & Choose the simplest viable method. Prefer recognition, symmetry, answer choices, or a known formula over a full setup. & One minimal setup: equation, diagram labels, coordinate rule, case labels, cycle list, or divisor condition.\\
35--65s & Check progress. & Continue only if expressions are shrinking, variables are canceling, or a known pattern is appearing. If not, pivot. & If pivoting, write the new method label, not a long explanation: ``test choices,'' ``mod 3,'' ``small cases,'' ``coordinates.''\\
65--100s & Finish or eliminate. & Decide whether the problem is becoming exact. If exact finish is not visible, use bounds, parity, modular checks, or answer testing. & Clean final computation or 2+ eliminated choices. Do not keep expanding a messy expression.\\
100--120s & Verify and commit. & Use a fast sanity check: magnitude, sign, integer/endpoint, units, probability between 0 and 1, or plug-back. & Circle the answer, write one check mark reason, or mark for return if confidence is too low.\\
\end{longtable}

\textbf{Teacher correction language.} When the student exceeds 2:00 on a correct Problem 10, the first question is not ``Why were you slow?'' Ask: ``Which 15-second trigger did you miss?'' Then identify the one cue that should have selected the shortcut.

\subsection{What Belongs on Scratch Paper vs. in the Head}

\begin{longtable}{@{}>{\raggedright\arraybackslash}p{0.24\textwidth} >{\raggedright\arraybackslash}p{0.34\textwidth} >{\raggedright\arraybackslash}p{0.34\textwidth}@{}}
\textbf{Category} & \textbf{Keep in the Head} & \textbf{Write on Scratch Paper}\\
\hline
Classification & Domain scan, confidence level, answer-choice shape, obvious one-step facts. & Domain tag, objective in 2--4 words, and the selected method cue.\\
Arithmetic & Single-operation facts: \(20\%=1/5\), \(25\%=1/4\), \(12^2=144\), \(13^2=169\), \(2^{10}=1024\), \(5!=120\). & Multi-step products, fractions that must be compared, modular cycles, and any calculation where a carry or sign could change the answer.\\
Algebra & Recognition of Vieta, completing square, SFFT, difference of squares, or substitution pattern. & The substitution, transformed equation, domain restrictions, and final simplified expression.\\
Geometry & Common triples, special angle ratios, diameter of a right-triangle circumcircle, and area/volume scaling rules. & Diagram, given labels, target quantity, coordinate rules, similarity ratios, and any hidden right triangle.\\
Counting/probability & Choice of complement, symmetry, expected value, or whether order matters. & Cases, sample space, restrictions, inclusion-exclusion terms, and the object being counted.\\
Number theory/sequences & Divisibility tests, parity, small mod choices, arithmetic/geometric recognition. & Congruences, periods, cycle lists, endpoint ranges, and recursive terms until a repeat appears.\\
\end{longtable}

\textbf{Write-it-down triggers.} The student should write immediately if there are more than two moving quantities, a sign or inequality reversal, a nested radical endpoint, a coordinate transformation, a counting case split, or a modular/cyclic pattern. These are working-memory traps; writing them down is faster than recovering from a missed condition.

\subsection{Mental Math Training Sequence}

Use mental math as a recognition and verification tool, not just as faster arithmetic. The student should practice these in short daily drills and then apply them inside timed problems.

\begin{longtable}{@{}>{\raggedright\arraybackslash}p{0.22\textwidth} >{\raggedright\arraybackslash}p{0.34\textwidth} >{\raggedright\arraybackslash}p{0.36\textwidth}@{}}
\textbf{Skill Block} & \textbf{Must-Know Mental Facts} & \textbf{AMC12 Speed Use}\\
\hline
Core values & Squares through \(25^2\), cubes through \(6^3\), powers of 2 through \(2^{10}\), factorials through \(7!\), common fractions \(1/3,1/4,1/5,1/6,1/8,1/9\). & Recognize answer magnitude and avoid writing small lookup facts.\\
Shortcut multiplication & \(\times 5,\times 9,\times 11,\times 15,\times 25,\times 125\); near-square products; \(a^2-b^2=(a+b)(a-b)\). & Compress routine calculations and identify factorizations quickly.\\
Percent/ratio sense & \(10\%\), \(5\%\), \(20\%\), \(25\%\), \(12.5\%=1/8\), \(33\frac{1}{3}\%=1/3\), \(62.5\%=5/8\). & Convert before/after percentage problems directly, as in row 14.\\
Algebra triggers & Vieta, completing square, hidden quadratic, SFFT, substitution \(x+1/x\), simple plug-in values \(0,1,-1,2\). & Choose a one-line setup instead of expanding.\\
Geometry triggers & \(3\!:\!4\!:\!5\), \(5\!:\!12\!:\!13\), \(8\!:\!15\!:\!17\), \(7\!:\!24\!:\!25\); \(30^\circ/45^\circ/60^\circ\); radius/diameter facts; area scales by \(k^2\). & Turn geometry into one remembered fact plus one proportional computation.\\
Number theory triggers & Mod 2, 3, 4, 5, 8, 9, 11; digit sums; units digit cycles; simple periods for powers and digit iterations. & Stop repeated computation once a cycle appears, as in row 10.\\
Counting/probability triggers & \(\binom{n}{2}=n(n-1)/2\), \(\binom{n}{3}=n(n-1)(n-2)/6\), complement, cases by parity/sign/range, probability bounds \(0\le P\le1\). & Prevent counting the wrong object and quickly reject impossible answers.\\
\end{longtable}

\textbf{Daily five-minute drill.} Spend 2 minutes on recall facts, 2 minutes on transformations, and 1 minute explaining one trigger aloud. Example: ``Odd number of consecutive integers means median equals mean,'' or ``right triangle in a circle means hypotenuse equals diameter.''

\subsection{Current Speed-Review Rows: Trigger Map}

\begin{longtable}{@{}>{\centering\arraybackslash}p{0.08\textwidth} >{\raggedright\arraybackslash}p{0.22\textwidth} >{\raggedright\arraybackslash}p{0.28\textwidth} >{\raggedright\arraybackslash}p{0.34\textwidth}@{}}
\textbf{Row} & \textbf{Trigger to Recognize} & \textbf{Keep in the Head} & \textbf{Write on Scratch Paper}\\
\hline
1 & 3D transformations as coordinate rules. & Reflections/rotations change signs or swap coordinates according to rule. & A three-column \(x,y,z\) sign table and the final transformed point.\\
7 & Odd consecutive list. & Median equals average. \(49=7^2\). & \(\text{median}=7^5/7^2=7^3\).\\
9 & Painted cube asks fraction of faces, not fraction of cubes. & Surface faces compare to all small-cube faces. & \(\frac{6n^2}{6n^3}=1/n=1/4\).\\
10 & Digit iteration sequence. & A repeat means period; stop computing linearly. & Terms until first repeat, then \((k-\text{first cycle index})\bmod \text{period}\).\\
13 & \(3:4:5\) right triangle in a circle. & Right triangle hypotenuse equals circle diameter. & Scale factor \(6/5\), then area computation.\\
14 & Total group size unchanged. & Girl fraction drops by \(10\%\); the drop is 2 girls. & \(0.10T=2\Rightarrow T=20\), then \(0.40T=8\).\\
\end{longtable}

\subsection{Pivot and Verification Rules}

\textbf{Pivot rule.} At 35 seconds, the student must be able to say what is getting simpler. If the answer is ``nothing,'' pivot immediately. Valid pivots are:
\begin{itemize}
  \item test answer choices after eliminating by magnitude, sign, parity, units, or domain;
  \item try a smaller case \(n=1,2,3\) to expose a pattern;
  \item switch representation: algebra to coordinates, geometry to ratios, counting to complement, sequence to cycle;
  \item use modular arithmetic, parity, or endpoints to reduce possibilities.
\end{itemize}

\textbf{Verification depth.} Match verification to the problem and clock:
\begin{itemize}
  \item \textbf{1--3 seconds:} gut check for sign, magnitude, integer requirement, probability range, or obvious endpoint.
  \item \textbf{5--10 seconds:} minimal sanity check for Q1--Q10: units, bounds, divisibility, and answer-choice consistency.
  \item \textbf{15--30 seconds:} targeted spot check for Q11--Q15 or any answer produced by a fragile computation: plug one value, check endpoint, or recalculate the riskiest line.
  \item \textbf{30+ seconds:} use only when the problem is high value or the student has extra time. Do not fully re-solve routine Problem 10 items.
\end{itemize}

\subsection{Teacher Practice Routine}

\begin{enumerate}
  \item \textbf{Recognition pass.} Give the student 15 seconds per problem. They must write only the domain tag, objective, and method cue. No solving.
  \item \textbf{Timed solve pass.} Re-solve the same problems with a 2:00 cap. Stop at 35 seconds to ask whether the path is shrinking. Stop at 65 seconds if no progress is visible.
  \item \textbf{Compression pass.} After each solution, require one trigger sentence and one computation line. Example: ``Odd consecutive list \(\Rightarrow\) median = mean; \(7^5/49=7^3\).''
  \item \textbf{Pattern log.} Record: source, domain tag, missed trigger, what stayed in head, what should have been written, time lost, faster method, and one follow-up drill.
  \item \textbf{Weekly review.} Consolidate repeated patterns into a small recognition library. Keep only high-yield signatures: the goal is 15--20 fast triggers the student can recall instantly, not a long formula sheet.
\end{enumerate}

\small
\begin{longtable}{@{}>{\raggedright\arraybackslash}p{0.05\textwidth} >{\raggedright\arraybackslash}p{0.26\textwidth} >{\centering\arraybackslash}p{0.08\textwidth} >{\centering\arraybackslash}p{0.08\textwidth} >{\centering\arraybackslash}p{0.08\textwidth} >{\centering\arraybackslash}p{0.08\textwidth} >{\raggedright\arraybackslash}p{0.17\textwidth}@{}}
\textbf{\#} & \textbf{Source} & \textbf{Stud.} & \textbf{Key} & \textbf{Time} & \textbf{Result} & \textbf{Note}\\
\hline
1 & 2000 AMC 12 P10 & E & E & 03:27 & \cmark & Over budget\\
2 & 2001 AMC 12 P10 & D & D & 01:09 & \cmark & Efficient\\
3 & 2002 AMC 12A P10 & D & D & 01:42 & \cmark & Efficient\\
4 & 2002 AMC 12B P10 & B & A & 01:45 & \xmark & Redo\\
5 & 2003 AMC 12A P10 & D & D & 01:23 & \cmark & Efficient\\
6 & 2003 AMC 12B P10 & B & B & 00:31 & \cmark & Very fast\\
7 & 2004 AMC 12A P10 & C & C & 03:58 & \cmark & Over budget\\
8 & 2004 AMC 12B P10 & A & A & 00:37 & \cmark & Very fast\\
9 & 2005 AMC 12A P10 & B & B & 05:14 & \cmark & Over budget\\
10 & 2005 AMC 12B P10 & E & E & 02:06 & \cmark & Slightly over\\
11 & 2006 AMC 12A P10 & D & E & 00:40 & \xmark & Redo\\
12 & 2006 AMC 12B P10 & A & A & 00:45 & \cmark & Very fast\\
13 & 2007 AMC 12A P10 & A & A & 02:10 & \cmark & Slightly over\\
14 & 2007 AMC 12B P10 & C & C & 03:05 & \cmark & Over budget\\
15 & 2008 AMC 12A P10 & D & D & 01:05 & \cmark & Efficient\\
\end{longtable}
\normalsize

\textbf{Completed score:} 13 correct out of 15 attempted, or \(86.7\%\). \textbf{Redo items:} rows 4 and 11. \textbf{Speed-review items:} rows 1, 7, 9, 10, 13, and 14.

\section{Speed-Review Solutions}

\subsection{Row 1: 2000 AMC 12 Problem 10}

\textbf{Answer:} E.

\textbf{Fast method.} Write each transformation as a coordinate rule instead of trying to visualize the whole 3D motion.
\[
(x,y,z)\xrightarrow{\text{reflect in }xy}(x,y,-z)
\xrightarrow{180^\circ\text{ about }x}(x,-y,-z)
\xrightarrow{+5\text{ in }y}(x,-y+5,-z).
\]
Applying this to \(P=(1,2,3)\) is fast:
\[
(1,2,3)\to(1,2,-3)\to(1,-2,3)\to(1,3,3).
\]

\textbf{Speed focus.} Use a three-column sign table: \(x\) unchanged, \(y\) changes only under the rotation and translation, and \(z\) changes under the reflection and rotation. This should be a 60--90 second problem once the rules are memorized.

\textbf{Speed-system application.}
\begin{itemize}
  \item \textbf{15-second trigger:} Geometry/3D transformation problem. Convert each motion into a coordinate rule instead of visualizing the whole solid.
  \item \textbf{Keep in the head:} Reflection in the \(xy\)-plane flips \(z\); a \(180^\circ\) rotation about the \(x\)-axis flips \(y\) and \(z\); translation changes only one coordinate.
  \item \textbf{Write on scratch:} A compact sign table or rule chain, then one application to \(P=(1,2,3)\).
  \item \textbf{35-second pivot:} If the picture feels confusing, stop drawing and switch to the coordinate table immediately.
  \item \textbf{Verification:} Two sign flips return \(z\) to positive, and the final \(y\)-coordinate is \(-2+5=3\).
\end{itemize}

\subsection{Row 7: 2004 AMC 12A Problem 10}

\textbf{Answer:} C.

\textbf{Fast method.} For an odd number of consecutive integers, the median equals the average. There are \(49=7^2\) integers and the sum is \(7^5\), so
\[
\text{median}=\frac{7^5}{49}=\frac{7^5}{7^2}=7^3.
\]

\textbf{Speed focus.} The key recognition is ``odd consecutive list \(\Rightarrow\) median = mean.'' Do not find endpoints. Pair terms around the center mentally, then divide sum by count.

\textbf{Speed-system application.}
\begin{itemize}
  \item \textbf{15-second trigger:} Sequence/statistics problem with an odd number of consecutive integers and a total sum.
  \item \textbf{Keep in the head:} Odd consecutive list means the center term equals the mean; \(49=7^2\).
  \item \textbf{Write on scratch:} Only \(\text{median}=\text{sum}/\text{count}=7^5/7^2=7^3\).
  \item \textbf{35-second pivot:} If endpoints are being computed, stop; endpoints are unnecessary for an odd consecutive list.
  \item \textbf{Verification:} The count is odd, so the median is an actual listed integer, not an average of two middle terms.
\end{itemize}

\subsection{Row 9: 2005 AMC 12A Problem 10}

\textbf{Answer:} B.

\textbf{Fast method.} Count faces, not small cubes. The total number of faces on all \(n^3\) unit cubes is \(6n^3\). The painted red faces are exactly the surface unit squares of the original cube, so there are \(6n^2\). Thus
\[
\frac{6n^2}{6n^3}=\frac{1}{n}=\frac14,
\]
so \(n=4\).

\textbf{Speed focus.} When a painted-solid problem asks for a fraction of faces, first compare ``surface area faces'' to ``all cube faces.'' Avoid classifying corner, edge, and face-center cubes unless the problem asks how many cubes have 1, 2, or 3 painted faces.

\textbf{Speed-system application.}
\begin{itemize}
  \item \textbf{15-second trigger:} Solid geometry/counting problem asking for a fraction of painted faces, not a count of painted cubes.
  \item \textbf{Keep in the head:} Surface of an \(n\times n\times n\) cube has \(6n^2\) exposed unit faces; all \(n^3\) small cubes have \(6n^3\) faces.
  \item \textbf{Write on scratch:} One unit-consistent ratio: \(\frac{6n^2}{6n^3}=1/n\).
  \item \textbf{35-second pivot:} If corner/edge/face-center cube cases appear, ask whether the problem counts cubes or faces. Here it counts faces, so abandon cube classification.
  \item \textbf{Verification:} Numerator and denominator both count unit-square faces; \(n=4\) gives \(1/4\), matching the given fraction.
\end{itemize}

\subsection{Row 10: 2005 AMC 12B Problem 10}

\textbf{Answer:} E.

\textbf{Fast method.} Compute only until a cycle appears:
\[
2005\to 2^3+5^3=133,\qquad
133\to 1^3+3^3+3^3=55,\qquad
55\to 5^3+5^3=250,
\]
and
\[
250\to 2^3+5^3=133.
\]
So from term 2 onward the cycle is \(133,55,250\), with period 3. Term 1 is outside the cycle, so for \(k\ge2\) index into \([133,55,250]\) by \((k-2)\bmod 3\). Since \(2005-2=2003\equiv2\pmod3\), the 2005th term is the third entry of the cycle, \(250\).

\textbf{Speed focus.} For digit-iteration sequences, do not continue linearly. Find the first repeat, write the cycle, then use modular arithmetic.

\textbf{Speed-system application.}
\begin{itemize}
  \item \textbf{15-second trigger:} Sequence problem asking for a far-out term under a repeated digit operation.
  \item \textbf{Keep in the head:} Cubes of small digits: \(1^3=1\), \(2^3=8\), \(3^3=27\), \(5^3=125\). A repeated value means the sequence has entered a cycle.
  \item \textbf{Write on scratch:} Terms only until the repeat: \(2005\to133\to55\to250\to133\), then the cycle and modular index.
  \item \textbf{35-second pivot:} If more than four terms are being generated without writing a cycle, stop and look for the first repeated value.
  \item \textbf{Verification:} The cycle starts at term 2 and has period 3, so use \((2005-2)\bmod 3\), not \(2005\bmod 3\).
\end{itemize}

\subsection{Row 13: 2007 AMC 12A Problem 10}

\textbf{Answer:} A.

\textbf{Fast method.} A \(3:4:5\) triangle is right, so its hypotenuse is the diameter of the circumcircle. The circle radius is 3, so the hypotenuse is 6. The scale factor from \(3:4:5\) is \(6/5\), giving legs
\[
\frac{18}{5}\quad\text{and}\quad \frac{24}{5}.
\]
The area is
\[
\frac12\cdot\frac{18}{5}\cdot\frac{24}{5}=\frac{216}{25}=8.64.
\]

\textbf{Speed focus.} For any right triangle in a circle, immediately use ``hypotenuse = diameter.'' This avoids trigonometry and side-solving.

\textbf{Speed-system application.}
\begin{itemize}
  \item \textbf{15-second trigger:} Geometry problem with a \(3:4:5\) triangle and a circumcircle.
  \item \textbf{Keep in the head:} \(3:4:5\) is right; a right triangle inscribed in a circle has hypotenuse equal to the diameter.
  \item \textbf{Write on scratch:} Diameter \(=6\), scale factor \(6/5\), legs \(18/5\) and \(24/5\), then area.
  \item \textbf{35-second pivot:} If trigonometry or side-solving begins, stop and use the diameter shortcut.
  \item \textbf{Verification:} The hypotenuse after scaling is \(5\cdot6/5=6\), exactly the circle diameter.
\end{itemize}

\subsection{Row 14: 2007 AMC 12B Problem 10}

\textbf{Answer:} C.

\textbf{Fast method.} The total group size does not change: two girls leave and two boys arrive. The fraction of girls drops from \(40\%\) to \(30\%\), a drop of \(10\%\) of the total group. That drop is exactly 2 girls, so
\[
10\%\text{ of total}=2 \quad\Rightarrow\quad \text{total}=20.
\]
Initially \(40\%\) of 20 were girls, so the answer is \(8\).

\textbf{Speed focus.} Compare the before/after percentages before setting up equations. If the total is unchanged, a percentage drop can be converted directly into a number of people.

\textbf{Speed-system application.}
\begin{itemize}
  \item \textbf{15-second trigger:} Percent-change word problem where the total group size stays fixed.
  \item \textbf{Keep in the head:} \(40\%-30\%=10\%\), and two girls leaving accounts for that entire \(10\%\) drop.
  \item \textbf{Write on scratch:} \(0.10T=2\Rightarrow T=20\), then \(0.40T=8\).
  \item \textbf{35-second pivot:} If two-variable equations for boys and girls are forming, check whether the total is unchanged and switch to percent-drop reasoning.
  \item \textbf{Verification:} Initially 8 girls out of 20 is \(40\%\); after two girls leave, 6 out of 20 is \(30\%\).
\end{itemize}

\section{Redo Solutions}

\subsection{Row 4: 2002 AMC 12B Problem 10}

\textbf{Correct answer:} A. The student chose B.

\textbf{Systematic method.} The set
\[
\{1,4,7,10,13,16,19\}
\]
is an arithmetic sequence. Every element has the form \(1+3k\), where \(k=0,1,2,3,4,5,6\). The sum of three distinct elements is
\[
(1+3a)+(1+3b)+(1+3c)=3+3(a+b+c).
\]
So different original sums correspond exactly to different values of \(a+b+c\), where \(a,b,c\) are distinct numbers chosen from \(0\) through \(6\).

The smallest possible index sum is \(0+1+2=3\), and the largest is \(4+5+6=15\). All values from 3 through 15 are possible, so there are
\[
15-3+1=13
\]
different sums.

\textbf{Methodology lesson.} For arithmetic-sequence choice problems, convert to indices and count the possible index sums. Do not count triples; many different triples can produce the same integer sum. Always separate ``number of selections'' from ``number of distinct values.''

\textbf{Speed-system application.}
\begin{itemize}
  \item \textbf{15-second trigger:} Counting problem with sums from an arithmetic sequence; the question asks for distinct values.
  \item \textbf{Keep in the head:} Arithmetic sequence terms can be replaced by indices; adding the same constant and scale factor preserves distinct sums.
  \item \textbf{Write on scratch:} \(1+3k\), then the minimum and maximum index sums: \(0+1+2=3\), \(4+5+6=15\).
  \item \textbf{35-second pivot:} If listing triples, stop and ask whether the question asks for selections or possible sum values.
  \item \textbf{Verification:} The index sums form every integer from 3 to 15, so the count is \(15-3+1=13\), not \(\binom{7}{3}\).
\end{itemize}

\subsection{Row 11: 2006 AMC 12A Problem 10}

\textbf{Correct answer:} E. The student chose D.

\textbf{Systematic method.} Let
\[
\sqrt{120-\sqrt{x}}=k,
\]
where \(k\) is a nonnegative integer. Then
\[
120-\sqrt{x}=k^2
\quad\Rightarrow\quad
\sqrt{x}=120-k^2.
\]
Since \(\sqrt{x}\ge 0\), we need \(120-k^2\ge 0\), so \(k^2\le 120\). The possible values are
\[
k=0,1,2,\ldots,10,
\]
because \(10^2=100\le120\) and \(11^2=121>120\). This gives 11 possible values of \(k\), and each one produces exactly one real value
\[
x=(120-k^2)^2.
\]

\textbf{Methodology lesson.} For nested radicals, name the whole expression first, then translate every square root into a domain inequality. Include endpoint cases: here \(k=0\) is valid, and missing it changes 11 to 10.

\textbf{Speed-system application.}
\begin{itemize}
  \item \textbf{15-second trigger:} Nested radical/counting-domain problem asking for how many real \(x\) values work.
  \item \textbf{Keep in the head:} If the outer square root is an integer \(k\), then \(k\ge0\), and \(11^2=121>120\).
  \item \textbf{Write on scratch:} Let \(\sqrt{120-\sqrt{x}}=k\), derive \(\sqrt{x}=120-k^2\), and write the endpoint inequality \(0\le k\le10\).
  \item \textbf{35-second pivot:} If solving for \(x\) directly becomes messy, return to the count of allowed integer \(k\) values.
  \item \textbf{Verification:} Check both endpoints: \(k=0\) gives \(x=120^2\), and \(k=10\) gives \(x=20^2\); both are valid.
\end{itemize}

\section{Student Strengths}

\begin{itemize}
  \item Strong accuracy on the attempted set: 13 out of 15 correct on mid-band Problem 10 material.
  \item Very fast execution on several algebra/geometry items: rows 6, 8, 11, and 12 were under one minute. Row 11 was wrong, but the speed shows the student is willing to commit; the next step is adding a quick endpoint check before bubbling.
  \item Good breadth across topics: coordinate geometry, ratios, sequences, counting, geometry, cube face counting, recursive digit process, inequalities, triangle geometry, and rate equations were mostly handled correctly.
\end{itemize}

\section{Growth Opportunities}

\begin{itemize}
  \item Add a 10-second classification step before solving: ``Am I counting choices, values, cases, or arrangements?'' This directly targets row 4.
  \item For radical/counting-domain problems, write the auxiliary variable and endpoint inequalities before answering. This directly targets row 11.
  \item Improve speed on straightforward recognition problems. Rows 1, 7, 9, 10, 13, and 14 were correct but over the 2-minute Q10 pace; each has a one-line shortcut once the problem type is recognized.
  \item Use a final ``endpoint and units'' check. For row 11, check both endpoints \(k=0\) and \(k=10\); an answer of 10 usually means one endpoint was dropped. For row 9, verify the numerator and denominator count the same object, unit-cube faces, before simplifying.
\end{itemize}

\section{Recommended Next Practice}

\begin{itemize}
  \item Redo rows 4 and 11 without looking at the solution, then explain the counting object in one sentence.
  \item Re-solve rows 1, 7, 9, 10, 13, and 14 with a 2:00 timer. The goal is not just to get the answer again, but to use the faster method.
  \item For future Problem 10 sets, pause at 1:30. If the path is not clear, switch to answer-choice testing, invariant recognition, or a simpler variable setup.
\end{itemize}

\end{document}
